DeepSphere: a graph-based spherical CNN

### 2019-09-23 main.tex
climate result tables

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
\end{itemize}
}
\newpage

@@

\todo{Graph, network architecture (info in the appendix, set the notation in the method section) and hyper-parameters. Or leave in appendix.}

\begin{table}%[ht]
    \centering
	\begin{tabular}{l cc r rS[table-format=2.0]}
		\toprule
		& \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
		& F1 & mAP & params & \multicolumn{1}{c}{inference} & \multicolumn{1}{c}{training} \\
		\midrule
		% $SO(3)$ vs $S^2$ vs graph
		\citet{cohen2018sphericalcnn} ($b=128$) & 78.9 & 67.6 & 1400\,k & 38.0\,ms & 50\,h \\
		\citet{cohen2018sphericalcnn} (simplified,\protect\footnotemark $b=64$) & 78.6 & 66.5 & 400\,k & 12.0\,ms & 32\,h \\
		\citet{esteves2018sphericalcnn} ($b=64$) & 79.4 & 68.5 & 500\,k & 9.8\,ms & 3\,h \\
		DeepSphere (equiangular $b=64$) & 79.4 & 66.5 & 190\,k & 0.9\,ms & 50\,m \\
		DeepSphere (HEALPix $N_{side}=32$) & 80.7 & 68.6 & 190\,k & 0.9\,ms & 50\,m \\
		\bottomrule
	\end{tabular}
    \caption{
		Results on SHREC'17 (3D shapes): DeepSphere achieves similar performance at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
		% F1-score computed with sklearn, mAP from the official script of the competition.
		% inference speed = time for a single instance to do a single training pass
		% training speed = time for the neural net to train to peak performance
	}
    \label{tab:shrec17}
\end{table}
\footnotetext[5]{As implemented in \url{https://github.com/jonas-koehler/s2cnn}.}

@@

\subsection{Climate event detection} \label{sec:exp:climate}

@@

\begin{table}
	\begin{tabular}{l|c c c c}
	\multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
	\cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5}
	\multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
	%Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
	\cite{jiang2019sphericalcnn} & 94.67 & - & - & -\\
	\cite{jiang2019sphericalcnn} \emph{rerun} & 94.95 & 38.41 & 10 & 10h\\
	% 328'339
	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 & - & -\\
	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 & - & -\\ \hline
	% unknown
	DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 33 & 13h \\
	DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 33 & 13h\\
	% 12'926'432
	\end{tabular}
	\caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang2019sphericalcnn}}
\end{table}

* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
* cross entropy loss between parenthesis\\
* 5 runs for each loss to obtain mean and std\\
* same architecture as gauge, more feature maps than Jiang\\
* perf with same arch as Jiang in appendix => not enough channels!\\
* even more feature maps give us one more point in perf\\
* cannot compare with Mudigonda: not the same input data\\
* why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling

@@

\begin{table}

\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy} & Size\\
        \cmidrule(lr){2-5} \cmidrule(lr){6-6}
        \multicolumn{1}{l}{Method} & TC & AR & BG & mean & params \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang2019sphericalcnn} & 94 & 93 & 97 & 94.67 & 330k\\
        \cite{jiang2019sphericalcnn} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95 & 330k\\
        % 328'339
        \cite{cohen2019gauge} (S2R) & 97.3 & 97.3 & 97.8 & 97.5 & -\\
        \cite{cohen2019gauge} (R2R) & 97.8 & 97.4 & 97.9 & 97.7 & -\\ \hline
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ & 13M\\
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ & 13M\\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 & 590k\\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 & 590k\\ \hline
        % 590k
        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 & 52M\\
        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 & 52M\\ \hline
        %DS-Cohen (weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
        %DS-Cohen (non-weighted) & 95.5 & 96.9 & 93.9 & 95.4 & 2M \\
        % DeepSphere (equi non-weighted) & 31.3 & 75.2 & 99.9 & 68.80
    \end{tabular}
    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
and AR classes plus mean accuracy.}
\end{table}

* DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}.\\
* DS-optimal has 2 times the number of feature maps of DS.\\

\begin{table}
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang2019sphericalcnn} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen2019gauge} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen2019gauge} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 33 & 13h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 33 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m \\ \hline
        % 590k
        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 & 50 & 20h \\
        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 & 50 & 20h \\ \hline
        %DS-Cohen (weighted) & 13.1 & 80.3 & 46.7 & 11 & 4h \\
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}

>>>>

\usepackage{hyperref}
\usepackage{url}
\usepackage{breqn}
\usepackage{booktabs}
\usepackage{siunitx} % used in SHREC table
\usepackage{bbm}        % for mathbbm
\usepackage{graphicx} \graphicspath{{figures/}}
%\usepackage{wrapfig}
%\usepackage{floatflt}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

@@

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
\end{itemize}
}
\newpage

@@

\todo{Graph (\#neighbors), network architecture (info in the appendix, set the notation in the method section) and hyper-parameters. Or leave in appendix.}

\begin{table}%[ht]
    \centering
	%\begin{tabular}{l cc r rr}
	\begin{tabular}{l cc r rS[table-format=2.0]}
		\toprule
		& \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
		& F1 & mAP & params & \multicolumn{1}{c}{inference} & \multicolumn{1}{c}{training} \\
		\midrule
		% $SO(3)$ vs $S^2$ vs graph
		\citet{cohen2018sphericalcnn} ($b=128$) & 78.9 & 67.6 & 1400\,k & 38.0\,ms & 50\,h \\
		\citet{cohen2018sphericalcnn} (simplified,\protect\footnotemark $b=64$) & 78.6 & 66.5 & 400\,k & 12.0\,ms & 32\,h \\
		\citet{esteves2018sphericalcnn} ($b=64$) & 79.4 & 68.5 & 500\,k & 9.8\,ms & 3\,h \\
		DeepSphere (equiangular $b=64$) & 79.4 & 66.5 & 190\,k & 0.9\,ms & 50\,m \\
		DeepSphere (HEALPix $N_{side}=32$) & 80.7 & 68.6 & 190\,k & 0.9\,ms & 50\,m \\
		\bottomrule
	\end{tabular}
    \caption{
		Results on SHREC'17 (3D shapes): DeepSphere achieves similar performance at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
		% F1-score computed with sklearn, mAP from the official script of the competition.
		% inference speed = time for a single instance to do a single training pass
		% training speed = time for the neural net to train to peak performance
	}
    \label{tab:shrec17}
\end{table}
\footnotetext[5]{As implemented in \url{https://github.com/jonas-koehler/s2cnn}.}

@@

\subsection{Climate event segmentation} \label{sec:exp:climate}

@@

\begin{table}
	\centering
	\begin{tabular}{l l l}
	\toprule
	& accuracy & mAP \\
	\midrule
	\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
	\cite{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 \\
	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 \\
	DeepSphere (weighted loss) & $97.8\pm 0.3$ & $77.15\pm 1.94$ \\
	DeepSphere (non-weighted loss) & $87.8\pm 0.5$ & $89.16\pm 1.37$ \\
	\bottomrule
	\end{tabular}
	\caption{
		Climate event segmentation results: mean accuracy and mean average precision (mAP). DeepSphere achieves state-of-the-art performance while using isotropic filters (S2S in \citet{cohen2019gauge}'s language), suggesting again that anisotropic filters are an unnecessary price to pay.
		Note that \citet{jiang2019sphericalcnn} and \citet{cohen2019gauge} use a weighted cross-entropy loss, which is good for the accuracy metric (as it corrects for class imbalance) but bad for the mAP metric.
	}
\end{table}

* icosahedron dataset from \cite{jiang2019sphericalcnn} \\
* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
* cross entropy loss between parenthesis\\
* 5 runs for each loss to obtain mean and std\\
* same architecture as gauge, more feature maps than Jiang\\
* perf with same arch as Jiang in appendix => not enough channels!\\
* even more feature maps give us one more point in perf\\
* cannot compare with Mudigonda: not the same input data\\
* why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling

@@

* DS-jiang is the similar architecture as \cite{jiang2019sphericalcnn}. \\
* DS-optimal has 2 times the number of feature maps of DS. \\
* \todo{What is DS and DS-Cohen?} \\
* \todo{Is (equi non-weighted) the full resolution?} \\
* \todo{check column order for DS} \\

\begin{table}
    \centering
	\begin{tabular}{l l l l l}
		\toprule
        & TC & AR & BG & mean \\
		\midrule
		\cite{mudigonda2017climateevents} & 74 & 65 & 97 & 78.67 \\
		\cite{jiang2019sphericalcnn} (paper) & 94 & 93 & 97 & 94.67 \\
		\cite{jiang2019sphericalcnn} (rerun) & 93.9 & 95.7 & 95.2 & 94.95 \\
        \cite{cohen2019gauge} (S2R) & 97.8 & 97.3 & 97.3 & 97.5 \\
        \cite{cohen2019gauge} (R2R) & 97.9 & 97.8 & 97.4 & 97.7 \\
		\midrule
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1 \\
        DS-optimal (weighted) & 91.5 & 93.4 & 99.0 & 94.6 \\
		\midrule
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5 \\
        DS-optimal (non-weighted) & 73.4 & 92.7 & 99.8 & 88.7 \\
		\midrule
		\todo{DS-Cohen (weighted)} & 95.5 & 96.9 & 93.9 & 95.4 \\
		\todo{DS-Cohen (non-weighted)} & 95.5 & 96.9 & 93.9 & 95.4 \\
		\todo{DeepSphere (equi non-weighted)} & 31.3 & 75.2 & 99.9 & 68.80 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: accuracy.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes, against the background (BG).
		\todo{\citet{mudigonda2017climateevents} is not directly comparable as they don't use the same input feature maps.}
		Note that a non-weighted cross-entropy loss is not optimal for the accuracy metric.
	}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{l l l l}
		\toprule
        & TC & AR & mean \\
		\midrule
		\cite{jiang2019sphericalcnn} (rerun) & 11.08 & 65.21 & 38.41 \\
        \cite{cohen2019gauge} (S2R) & - & -& 68.6 \\
        \cite{cohen2019gauge} (R2R) & - & -& 75.9 \\
		\midrule
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ \\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 \\
        DS-optimal (non-weighted) & 84.71 & 98.05 & 91.38 \\
		\midrule
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ \\
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 \\
        DS-optimal (weighted) & 52.80 & 94.78 & 73.79 \\
		\midrule
		\todo{DS-Cohen (weighted)} & 13.1 & 80.3 & 46.7 \\
		\todo{DeepSphere (equi non-weighted)} & 55.53 & 94.85 & 75.19 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: average precision.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes.
		Note that a weighted cross-entropy loss is not optimal for the average precision metric.
	}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{l r r r}
		\toprule
		& \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed} \\
        \cmidrule(lr){2-2} \cmidrule(lr){3-4}
		& params & inference & training \\
		\midrule
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
		\cite{jiang2019sphericalcnn} & 330\,k & 10\,ms & 10\,h \\ % 328'339
		% \cite{cohen2019gauge} (S2R) & - & - & - \\
        % \cite{cohen2019gauge} (R2R) & - & - & - \\
		DeepSphere (Jiang) & 590\,k & 5\,ms & 3\,h \\ % 590k
        DeepSphere & 13\,M & 33\,ms & 13\,h \\ % 12'926'432
		DeepSphere (optimal) & 52\,M & 50\,ms & 20\,h \\
		\todo{DS-Cohen (weighted)} & 2\,M & 11\,ms & 4\,h \\
		\todo{DeepSphere (equi non-weighted)} & - & 567\,ms & 48\,h \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: size and speed.
	}
\end{table}
